Dynein notes

### 2017-10-21 reorganize/papers/notes/notes.tex
Add schmidt paper to notes.tex

\section{Papers}
\subsection{Tension on the Linker Gates the ATP-Dependent Release of Dynein from Microtubules - Yildiz 2014}
Yildiz shows that dynein only requires one functional head, and an MTBD linker, to walk. He claims that this shows dynein relies on high bb/ob time, not from communication. He does say that linker tension increases ATP hydrolysis rate, which isn't really inter-head connection.\\
Takeaway: linker tension inhibits MT release. Stepping happens lots when the active head is low-tension (near its partner), but not when it is far away.\\

>>>>

\section{Papers}
\subsection{Structure of human cytoplasmic dynein-2 primed for its power stroke}
Schmidt, Carter et al\\

Paper on crystallizing dynein-2 (cytoplasmic) with and without ADP-Vanadate to find the pre- and post-powerstroke structures. They find a different foot-head-tail angle than the Burgess paper (possibly because Burgess crystallized axonemal dynein). Burgess found a ~20 degree shift for axonemal, and schmidt found a 90 degree shift in angle on pre-stroking.\\

\subsection{Tension on the Linker Gates the ATP-Dependent Release of Dynein from Microtubules - Yildiz 2014}
Yildiz shows that dynein only requires one functional head, and an MTBD linker, to walk. He claims that this shows dynein relies on high bb/ob time, not from communication. He does say that linker tension increases ATP hydrolysis rate, which isn't really inter-head connection.\\
Takeaway: linker tension inhibits MT release. Stepping happens lots when the active head is low-tension (near its partner), but not when it is far away.\\
